%-------------------------
% Resume in Latex
% Author : Subham Goyal
% License : IIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{home.iitk.ac.in/~subhamg/}{\Large Subham Goyal}} & Email : \href{mailto:goyalsubham.iitk@gmail.com}{goyalsubham.iitk@gmail.com}, \href{mailto:subhamg@iitk.ac.in}{subhamg@iitk.ac.in}\\
  \href{https://github.com/subhamg}{https://github.com/subhamg} & Mobile : +91-8948340341, 8887042140 \\
\end{tabular*}

\vspace{-3mm}
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology, Kanpur}{2018 (Expected)}
      {B.Tech in Material Science and Engineering}{Undergraduate CGPA: 5.9}
      \vspace{-1.5mm}
    \resumeSubheading
      {Green Wood Public School, Sitarganj}{1997-2012}
      {All India Senior and Senior Secondary School Certificate (CBSE)}{XII std : 92\%, X std : 97.8\%}
  \resumeSubHeadingListEnd
\vspace{-6mm}
%-----------Scholastic Achievements------------
\section{Scholastic Achievements}
  \resumeSubHeadingListStart
    \item \small{Secured certificate for developing windows app and completing the \textbf{Code.fun.do} student hackathon organized by Microsoft at IIT Kanpur on Jan 30-feb 1, 2015.}
    \vspace{-3mm}
    \item \small{Secured \textbf{All India Rank 6 ph.} in Join Entrance Examination'12 among 5 lakh candidates}
    \vspace{-3mm}
   \item \small{Secured \textbf{All State Rank 3} in first round of \textbf{10th National Science Olympiad} with a percentile score of 99.08.}
   \vspace{-3mm}
   \item \small{Secured \textbf{All India Rank 1053} in second round of \textbf{10th National Science Olympiad}.}
  \resumeSubHeadingListEnd
  \vspace{-7mm}
%-----------WORK EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart
  
  \resumeSubheading
      {New York Office, IIT Kanpur}{(Kanpur, UP)}
      {Front End Developer and UX/UI Designer}{May 2016 - Present}
      \resumeItemListStart
      \item
          \small{Summer Internship continued as a volunteer and peer mentor}
            \vspace{-1.5mm}
        \item
          \small{Continuous implementation and integration of new features on a scalable microservice-based web application with an extensive technology stack.}
            \vspace{-1.5mm}
          \item
          \small{Implemented an Angular application as per the Redux architecture (NgRx) for easy extensibility and modularity.}
            \vspace{-1.5mm}
          
        \item
        \small{ Implemented Reactions, Hover-card, Global trends, Multi-thread comment \& Prose-Mirror into an existing App.}
        \vspace{-1.5mm}
          \item
          \small{Created and usability tested wireframes, UX flows, motion design, prototypes \& visual polish of an entire application using Photoshop, Illustrator, Adobe XD etc. }
           \vspace{-1.5mm}
          \item
          \small{Researched, designed and validated workflows \& interfaces through iterations for a more approachable \& valuable experience. }
      \resumeItemListEnd
      
      \resumeSubheading
      {Aeon Logiciel}{(Noida, UP)}
      {Full Stack Developer}{Dec 2017}
      \resumeItemListStart
        \item
          \small{Worked to build and establish an e-commerce platform using the Laravel framework.}
            \vspace{-1.5mm}
          \item
          \small{Implemented RestFul API, Oauth authentication \& authorization between multiple systems, Payment portal, etc.}
            
      \resumeItemListEnd

    \resumeSubheading
      {Tourepedia}{(Kanpur, UP)}
      {UX/UI Designer}{Nov 2013 - Dec 2013}
      \resumeItemListStart
        \item
          \small{Developed user-centred  design methodology, direct overall Web UI design and usability strategies for tourepedia.com online shopping Web application.}
            \vspace{-1.5mm}
          \item
          \small{Designed marketing materials like advertisements, brochures, handouts, flyers and online graphics etc.}
            \vspace{-1.5mm}
          \item
          \small{Collaborated on user experience planning with a lead experience architect.}
            \vspace{-1.5mm}
        \item
        \small{Prototyped responsive HTML5 and CSS3 prototypes with the Bootstrap 3 framework. }
        \vspace{-1.5mm}
          \item
          \small{Created wireframes, mock-ups, task flows, logos, icons and UI specifications as needed for other applications using Adobe Illustrator and Photoshop software.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Localities}{(Kanpur, UP)}
      {Freelance, Full Stack Developer}{}
      \resumeItemListStart
        \item
          \small{Worked on a web application to easily share data between different moderators using the MEAN stack.}
            \vspace{-1.5mm}
          \item
          \small{Created RestFul API using NodeJs and Express Framework.}
          \vspace{-1.5mm}
          \item
          \small{Designed and Developed many single page web application from scratch as a freelancer.}
            
      \resumeItemListEnd
    
    \resumeSubheading
      {Jan Jagriti Seva Samiti- NGO}{(Rudrapur, UK)}
      {Social Worker}{Nov 2013 - Dec 2013}
      \resumeItemListStart
        \item
          \small{Participated in Awareness Camp for blind patient, training programs and other events as appropriate and needed.}
            \vspace{-1.5mm}
          \item
          \small{Completed timely documentation, and actively participated in team meetings.}
            \vspace{-1.5mm}
          \item
          \small{Collaborated with hospice medical staff to establish and modify, when necessary, client focused hospice services.}
            \vspace{-1.5mm}
          \item
          \small{Developed and maintained contact with appropriate community agencies and services in order to promote interagency cooperation and to facilitate related referrals.}
      \resumeItemListEnd
      

  \resumeSubHeadingListEnd
\vspace{-6mm}

%-----------MAJOR POSITION-----------------
\section{Major Position of Responsibility}
  \resumeSubHeadingListStart
  
   \resumeSubheading
      {Udghosh'17}{ (Inter-Collegiate Sports Festival)}
        {Core Team Member - Head Web and Android}{Apr 2017 - Present}
      \resumeItemListStart
        \item
          \small{ Designed and Developed the festival’s portal responsible for the registration of more than 2300 participants using \textbf{PHP} and \textbf{SQL}.}
            \vspace{-1.5mm}
          \item
          \small{Developed the official website for the sports festival  Udghosh of IIT Kanpur using \textbf{HTML,CSS, Java Script}.}
            \vspace{-1.5mm}
          \item
          \small{Managing various events and activities and playing an important role in taking decisions regarding the festival}
            \vspace{-1.5mm}
        \item
        \small{ Working on native \textbf{android} development to create Udghosh android application. }
        \vspace{-1.5mm}
          \item
          \small{Integrated \textbf{Firebase}  to Store and sync data in realtime across all connected clients.}
        
        \vspace{-1.5mm}
          \item
          \small{ Collaborated with YouWeCan to spread awareness about Cancer and raised a fund of 1 Million}
          \vspace{-1.5mm}
          \item
          \small{Organized Cyclothon witnessing Chief Guest \textbf{Nuzhat Parween}.}
          
      \resumeItemListEnd
      
 \resumeSubheading
      {Inter IIT Sports Meet 2016}{ }
        {Core Team Member - Head Web and Android}{May 2016 - Dec 2016}
      \resumeItemListStart
        \item
          \small{Spearheaded a 2-tier team of web developers and worked closely with other members to develop detailed specifications of the event.}
            \vspace{-1.5mm}
          \item
          \small{Involved in Responsive Web designing and development using \textbf{HTML, CSS3, JavaScript, jQuery} etc.}
            \vspace{-1.5mm}
          \item
          \small{Involved in \textbf{database design} and writing queries for many modules using \textbf{MySQL}.}
            \vspace{-1.5mm}
        \item
        \small{Developed internal event web applications for live updates in PHP. Designed imaginative and colorful website. }
        \vspace{-1.5mm}
          \item
          \small{ Designed and developed an \textbf{Android app} with an intuitive design and real time sync to keep one updated.}
        
        \vspace{-1.5mm}
          \item
          \small{ Implemented Fragments, List Views, and material design principles to create a great user experience}
          \vspace{-1.5mm}
          \item
          \small{Associated with Raktarpan to organize a Blood Donation and Mini- Health Checkup Camp for IIT Kanpur.}
          \vspace{-1.5mm}
          \item
          \small{Connected with “Impact Run” and “Flush Mob” to propel Pan IIT Fitness and Sanitation Drives.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Udghosh'15}{( Inter-Collegiate Sports Festival)}
        {Core Team Member - Head Design}{Apr 2015 - Oct 2015}
      \resumeItemListStart
        \item
          \small{Led a 2-tier Design Team for successful conduction of Festival with more than 1800 participants Nationwide.}
            \vspace{-1.5mm}
          \item
          \small{Conceptualised the idea for a Countdown to the Festival, a new logo, branding avenues and doodle for Udghosh.}
            \vspace{-1.5mm}
          \item
          \small{Coordinated with 20 heads of their respective cells and met their deadline to release the merchandise design.}
            \vspace{-1.5mm}
        \item
        \small{Used typography, imagery and creative concepts to give Udghosh a visual feast. }
        \vspace{-1.5mm}
          \item
          \small{Managed promotions of Festival over mass media comprising Dainik Jagran, Facebook \& Twitter.}
          \vspace{-1.5mm}
          \item
          \small{Successfully planned and organised Events on Social Media like Xperience 9, Smash-D-Dub.}
      \resumeItemListEnd
      
    
   
      

  \resumeSubHeadingListEnd
\vspace{-7mm}

%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
  \resumeSubHeadingListStart
  \small{
  \item{
      \textbf{Packages}{: Sketch, Photoshop, Adobe XD, Illustrator, After Effects, Premiere Pro, AutoCAD, MATLAB, LaTex}}
      \vspace{-2.5mm}
    \item{
      \textbf{Languages}{: C, C++, Python, Java, NodeJs, Golang, Kotlin}
      }
     
       \vspace{-2.5mm}
      \item{
      {\textbf{Web}{: HTML, CSS, SASS, PHP, JavaScript, SQL, TypeScript, REST API}}}
       \vspace{-2.5mm}
       \item{
       \textbf{Utilities}{: Bash, Git, MongoDB, Numpy, OpenCV, Firebase, AWS, Zepline, MS Office, MS Azure, Android Studio }
       }
       \vspace{-2.5mm}
    \item{
    \textbf{Frameworks}{: Angular, Express, Django, React.Js, Laravel, Truffle}
      \hspace{5mm}
    $\bullet$ {\textbf{Platform}}{: Windows, Linux, Android, Mac }
      \hfill
        }}
      
      
  \resumeSubHeadingListEnd
  
  \vspace{-7mm}
%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
  \resumeSubheading
      {Costa Rican Household Poverty Level Prediction }{(IIT Kanpur)}
        {Prof. Faiz Hamid}{May 2019 - Jun 2019}
      \resumeItemListStart
        \item
          \small{Developed a supervised classification model to predict household proverty level}
            \vspace{-1.5mm}
          \item
          \small{Performed  Exploratory Data Analysis (EDA), dimensionality reduction, feature engineering and encoded categorical variables to prepare Dataset for machine learning}
            \vspace{-1.5mm}
          \item
          \small{Compared several baseline machine learning models such as Classification Method, Logistic Regression and Neural Networks to see which one is most promising}
          \vspace{-1.5mm}
          \item
          \small{Optimization and implementation of the best performing model and tune}\\
      {\textbf{Technologies}}{: Python, Jupiter}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  \vspace{-5mm}
\resumeSubHeadingListStart
  \resumeSubheading
      {Ethereum Healthcare DApp }{(IIT Kanpur)}
        {Prof. Sandeep Shukla}{Jan 2018 - Apr 2018}
      \resumeItemListStart
        \item
          \small{Build decentralized and cryptographically empowered database system to tackle the problem of unavailability of authentic past health records of a person.}
            \vspace{-1.5mm}
          \item
          \small{Employed Ethereum to incorporates the business logic and technical details into a single smart contract.}
            \vspace{-1.5mm}
            \item
          \small{Connected D-App with smart contracts using web3.js - a open source library }
          \vspace{-1.5mm}
          \item
          \small{Compiled and deployed smart contracts over Blockchain Ethereum network using Truffle Framework}
           \vspace{-1.5mm}
          \item
          \small{Stored electronic health records of all users in a database using symmetric key cryptography}\\
          {\textbf{Technologies}}{: Metamask, Truffle, NodeJS, Solidity, Web3.js, Ganache-cli}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  \vspace{-5mm}
\resumeSubHeadingListStart
  \resumeSubheading
      {LAMMPS }{(IIT Kanpur)}
        {Prof. Nilesh Gurao}{July 2016 - Dec 2016}
      \resumeItemListStart
        \item
          \small{Used Molecular dynamics tool LAMMPS to determine elastic properties of metals}
            \vspace{-1.5mm}
          \item
          \small{Created a box of atoms in face centre cubic copper for different orientations}
            \vspace{-1.5mm}
          \item
          \small{Block was subjected to normal stresses to obtain elastic properties of copper.}
          \vspace{-1.5mm}
          \item
          \small{Compared the simulation results with experimental observations.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  \vspace{-5mm}
  \resumeSubHeadingListStart
  \resumeSubheading
      {Kinetic Sculpture of Wing }{(IIT Kanpur)}
        {Prof. Shashank Shekhar}{Jan 2015 - Apr 2015}
      \resumeItemListStart
        \item
          \small{Received a \textbf{Merit certificate} of appreciation for design and fabrication of the project, submitted as the partial fulfillment of the course Introduction to Manufacturing Process (TA-201).}
            \vspace{-1.5mm}
          \item
          \small{Project was under Metallurgical Manufacturing Process course and involved various types of metallurgical processes like sand casting, grinding, welding, sheet-metal forming, and brazing.}
            \vspace{-1.5mm}
          \item
          \small{The kinetic sculpture is made with sheet metal, replicated a bird flapping its wings using simple machines and materials.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  \vspace{-7mm}
  
  %
%--------Extra Co-curricular activities------------
\section{Relevant Courses}
  \small{
    $\circ$ Data Mining and Knowledge Discovery \hfill
    $\circ$ Blockchain Technology and Application \hfill
    $\circ$ Computer System and Security \hspace{15mm}
    $\circ$ Fundamentals of Computing \hspace{25mm}
    }


%-------------------------------------------
%
%--------Extra Co-curricular activities------------
\section{Extra-Curricular Activities}
  \resumeSubHeadingListStart
  \small{
    \item{
      \textbf{Technology}{: Participated in robotics event ,Takneek'13 (Institute)\\ \hspace{2.3cm}Participated in event organized by astronomy club, Takneek'13 (Institute)\\ \hspace{2.3cm}Solved 3x3x3 Rubik’s cube, Takneek’13(Institute)}}
      \vspace{-3mm}
       \item{
      \textbf{Films and Media}{: Appointed to the post of Secretary, Photography club\\ \hspace{3.3cm}Worked in a team of over 20 individuals to successfully organize the Hall level workshops.\\ \hspace{3.3cm}Covered both technical and cultural fest of IIT Kanpur i.e. Techkriti’14 and Antaragni’14}}
         \vspace{-3mm}
       \item{
      \textbf{National Service Scheme}{: Published Ek Sparsh Prakriti ka Magazine under Prof. H.C.Verma\\ \hspace{4.7cm}Convinced teachers and students of different schools to participate in competition.}}}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
